Models

### 2022-12-07 analysis/05_model_metrics.Rmd
Add bootstrap approach for calculating study slopes

>>>>

Get study level slopes using bootstrap resampling
```{r}
extract_study_slopes <- function(model){

  #get the statistics for the year variable
  year_scaled_est <- tidy(model) %>%
    filter(term == "year_scaled") %>%
    pull(estimate)

  estimate <- broom.mixed::tidy(model, effects="ran_vals") %>%
    filter(group == "study_id", term == "year_scaled") %>% 
    select(-c(effect, group, term)) %>%
    rename(cond.estimate = estimate) %>%
    mutate(estimate = cond.estimate + year_scaled_est) %>%
    select(level, estimate) %>%
    deframe()

  return(estimate)
}

bootstrap_study_slopes <- function(metric, model, model_id, nsim){
  print(c(metric, model_id))

  fric_vars <- bootMer(model, FUN = extract_study_slopes, nsim = nsim, use.u = TRUE)

  estimates <- enframe(fric_vars$t0, name = "study_id", value = "estimate")

  as_tibble(fric_vars$t) %>% 
    pivot_longer(everything(), names_to = "study_id", values_to = "values") %>%
    group_by(study_id) %>%
    summarize(n = n(), std.error = sd(values)/sqrt(n)) %>%
    left_join(estimates) %>%
    select(-n) %>%
    mutate(metric = metric, model_id = model_id)
}

#future::plan("multisession", workers = 30)

bootstrap_slopes <- pmap_dfr(model_df %>% filter(model_id == "base") %>% mutate(nsim = 100), bootstrap_study_slopes) %>%
  # furrr::future_pmap_dfr(model_df %>% filter(model_id == "base") %>% mutate(nsim = 100), bootstrap_study_slopes, 
  #                                          .options = furrr::furrr_options(seed = TRUE)) %>%
  mutate(upr.ci = estimate + (2*std.error),
         lwr.ci = estimate - (2*std.error),
         sig = case_when(
             lwr.ci < 0 & upr.ci > 0 ~ FALSE,
             TRUE ~ TRUE
           ))
```
